---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(magrittr)
library(dplyr)
```

# brcaClinical

<!-- badges: start -->
<!-- badges: end -->

This package contains clinical data from `r nrow(brcaClinical::brca_clinical)` breast cancer studies obtained from [cBioPortal](https://cbioportal.org):

```{r}
library(brcaClinical)
brca_clinical[, c('studyId', 'name')]
```

## Usage

The clinical data for each study can be found at the last column of `brca_clinical`: `clinicalData`.

As an example, to have a glimpse at a few selected variables of the clinical data from the METABRIC project:

```{r}
library(brcaClinical)

metabric_clinical <- brca_clinical$clinicalData$brca_metabric
dplyr::select(metabric_clinical,
              patientId,
              AGE_AT_DIAGNOSIS,
              HISTOLOGICAL_SUBTYPE)
```

## Installation

```R
# Install the released version from CRAN
install.packages("brcaClinical")

# Install the development version from GitHub
devtools::install_github("maialab/brcaClinical")
```

## Contributors

Please note that the brcaClinical project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

