---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(magrittr)
library(dplyr)
```

# brcaClinical <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
[![License: CC BY-SA 4.0](https://img.shields.io/badge/license-CC%20BY--SA%204.0-%2300AED3)](https://creativecommons.org/licenses/by-sa/4.0/)
[![Source: cBioPortal](https://img.shields.io/badge/source-cBioPortal-%233786C2)](https://www.cbioportal.org/)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Overview

This package contains clinical data from `r nrow(brcaClinical::brca_clinical)` breast cancer studies obtained from [cBioPortal](https://cbioportal.org):

```{r}
library(brcaClinical)
brca_clinical[, c('studyId', 'name')]
```

## Usage

The clinical data for each study can be found at the last column of `brca_clinical`: `clinicalData`.

As an example, to have a glimpse at a few selected variables of the clinical data from the METABRIC project:

```{r}
library(brcaClinical)

metabric_clinical <- brca_clinical$clinicalData$brca_metabric
dplyr::select(metabric_clinical,
              patientId,
              AGE_AT_DIAGNOSIS,
              HISTOLOGICAL_SUBTYPE)
```

## Installation

```R
# Install the development version from GitHub
devtools::install_github("maialab/brcaClinical")
```

## Code of Conduct
  
Please note that the brcaClinical project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## License

CC BY-SA 4.0, plus see [LICENSE](LICENSE) for the licenses of the
individual data sets.
